Detecting social information in a dense dataset of infants’ natural visual experience

### 2020-01-24 paper/cogsci/paper.Rmd
most recent versions of markdown and pdf for cogsci paper

@@

```{r}
d_by_location_cropped <- d_cropped %>%
  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
  mutate(age_day_bin = as.numeric(as.character(age_day_bin))) %>%
  left_join(meta) %>%
  filter(!is.na(Location)) %>%
  filter(count_locations==1) 
# 
# d_by_location_cropped$Location = droplevels(d_by_location_cropped$Location)
# levels(d_by_location_cropped$Location)

>>>>

```{r eval=FALSE}
summary_by_age_days_cropped_limited <- d_cropped %>%
  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
  mutate(age_day_bin = as.numeric(as.character(age_day_bin))) %>%
  group_by(age_day_bin,child_id) %>%
  filter(age_day_bin < (24))  %>%
  summarize(num_faces = sum(face_openpose), num_hands = sum(hand_detected_cropped)) %>%
  rename(age_months = age_day_bin)

summary_by_age_days_cropped <- d_cropped %>%
  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
  mutate(age_day_bin = as.numeric(as.character(age_day_bin))) %>%
  group_by(age_day_bin,child_id) %>%
  summarize(num_faces = sum(face_openpose), num_hands = sum(hand_detected_cropped)) %>%
  rename(age_months = age_day_bin)

```{r eval=FALSE}
### Proportion faces vs. hands 
face_vs_hands_model_limited <- glmer(cbind(num_faces,num_hands) ~ scale(age_months) + (1 | child_id), 
             summary_by_age_days_cropped_limited, family = "binomial")
# doesn't converge with random slopes for age | child_id
face_vs_hands_model_limited_out = summary(face_vs_hands_model_limited)

```{r eval=FALSE}
### Proportion faces vs. hands 
face_vs_hands_model_full_age <- glmer(cbind(num_faces,num_hands) ~ scale(age_months) + (1 | child_id), 
             summary_by_age_days_cropped, family = "binomial")
# doesn't converge with random slopes for age | child_id
face_vs_hands_model_full_age_out <- summary(face_vs_hands_model_full_age)

# xtable(face_vs_hands_model_full_age_out$coefficients, digits=c(2,2,2,2,3),"Model coefficients from a generalized linear mixed model predicting the proportion of faces vs. hands seen by infants.") 
```

\begin{table}[ht]
\centering
\begin{tabular}{rrrrr}
  \hline
 & Estimate & Std. Error & z value & Pr($>$$|$z$|$) \\ 
  \hline
(Intercept) & -0.26 & 0.09 & -2.83 & 0.005 \\ 
  scale(age\_months) & -0.15 & 0.00 & -225.40 & 0.000 \\ 
   \hline
\end{tabular}
\caption{Model coefficients from a generalized linear mixed model predicting the proportion of faces vs. hands seen by infants.} 
\end{table}

@@

```{r}
d_by_location_cropped <- d_cropped %>%
  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
  mutate(age_day_bin = as.numeric(as.character(age_day_bin))) %>%
  left_join(meta) %>%
  filter(!is.na(Location)) %>%
  filter(count_locations==1) 
#

# d_by_location_cropped$Location = droplevels(d_by_location_cropped$Location)
# levels(d_by_location_cropped$Location)
